---
title: "Conclusion"
format:
  html: 
    toc: false
    link-external-icon: false
    link-external-newwindow: false
---

```{r include = FALSE}
source(here::here("R", "buttons.R"))
```

Congratulations! You've completed the *First Steps* module!

## Learning Goals

Now that you've completing this module, you should be able to:

### Basic Commands

1. Create simple R objects
1. Conduct simple mathematical calculations involving R objects
1. Conduct simple logical comparisons between R objects

### R Functions

1. Recognize the R functions in a section of R code
1. Give a conceptual overview of how R functions operate
1. Call R functions to perform calculations on R objects

### Add-On Packages

1. Explain the procedure required to install, load, and use an R package
1. Install new R packages from a remote package repository
1. Load an R package
1. Use the functions provided by add-on packages

### Getting Help

1. Access the documentation for functions provided by installed packages
1. Explain the purpose of the sections in an R help file
1. Use the information in an R help file to learn how to use an unfamiliar R function

## Next Steps

If you want to continue with your R learning journey, we recommend following the *Data Types* module next. Click the 
button below to start the next module.

```{r}
#| echo: false
#| results: asis
next_module_button("/in_progress.html")
```
