---
title: "First Steps"
format:
  html: 
    toc: false
    section-divs: true
    include-after-body: 
      - text: |
          <script src="/js/progressive-reveal.js"></script>
          <script src="/js/bootstrapify.js"></script>
---

```{r include = FALSE}
source(here::here("R", "helpers.R"))
```
Welcome to the *First Steps* module. In this module, you will take the first steps in your R programming journey by
learning the basics of R usage. The module content is broken into three tutorials:

- [Basic Commands](/sections/01_basic_commands.qmd)
- [Add-On Packages](/sections/02_packages.qmd)
- [Getting Help](/sections/03_help.qmd)

## Learning Goals

### Basic Commands

1. Blah
1. Blah, blah
1. Blah, blah, blah

### Add-On Packages

1. Blah
1. Blah, blah
1. Blah, blah, blah

### Getting Help

1. Blah
1. Blah, blah
1. Blah, blah, blah

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_buttons("/sections/01_basic_commands.html")
```
