---
title: "First Steps"
format:
  html: 
    toc: false
    page_navigation: false
---

```{r include = FALSE}
source(here::here("R", "helpers.R"))
```

Welcome to the *First Steps* module. In this module, you will take the first steps in your R programming journey by
learning the basics of R usage. The module content is broken into four tutorials:

1. [Basic Commands](/tutorials/basic_commands/index.qmd)
1. [R Functions](/tutorials/functions/index.qmd)
1. [Add-On Packages](/tutorials/packages/index.qmd)
1. [Getting Help](/tutorials/help/index.qmd)

Each tutorial will comprise a series of interactive lessons with practice problems embedded throughout. After you complete
each tutorial, you will have the opportunity to complete a knowledge quiz to check your learning.

## Learning Goals

After completing this module, you will be able to:

### Basic Commands

1. Create simple R objects
1. Conduct simple mathematical calculations involving R objects
1. Conduct simple logical comparisons between R objects

### R Functions

1. Recognize the R functions in a section of R code
1. Give a conceptual overview of how R functions operate
1. Call R functions to perform calculations on R objects

### Add-On Packages

1. Explain the procedure required to install, load, and use an R package
1. Install new R packages from a remote package repository
1. Load an R package
1. Use the functions provided by add-on packages

### Getting Help

1. Access the documentation for functions provided by installed packages
1. Explain the purpose of the sections in an R help file
1. Use the information in an R help file to learn how to use an unfamiliar R function

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_buttons("/tutorials/basic_commands/index.html")
```
