---
title: "Help File Sections"
webr:
  packages:
    - dplyr
---

```{r setup, echo = FALSE, include = FALSE}
library(printr)
```

R help files can contain diverse information: some are only a few lines long while others contain dozens of pages of 
information. Not all R help files include all possible sections, but there are a few core sections that tend to show up
pretty consistently due to their general usefulness.

## Description 

```{=html}

{{< include /assets/docs/arrange_description.html >}}

```

As the name implies, the *Description* section provides a brief, human-readable description of the functions purpose.

## Usage

```{=html}

{{< include /assets/docs/arrange_usage.html >}}

```

The *Usage* section shows the fully parameterized function call. In other words, how to call the function. In particular,
this section provides several crucial pieces of information.

- The name used to call the function
- The name of all the function arguments
- The order of the function arguments
- Any default values defined for function arguments

## Arguments

```{=html}

{{< include /assets/docs/arrange_arguments.html >}}

```

The *Arguments* section briefly explains each function argument. As you might suspect, the arguments section will probably
be the one you reference most frequently since the information contained herein explains the purpose or each function
argument and what type of values you are able to specify for each argument.

## Details

```{=html}

{{< include /assets/docs/arrange_details.html >}}

```

The *Details* section expands on the information listed in the *Arguments* section to provide additional details of
function arguments or the functions behavior

## Value

```{=html}

{{< include /assets/docs/arrange_value.html >}}

```

The *Value* section describes the type of object returned by the function.

## Examples

```{=html}

{{< include /assets/docs/arrange_examples.html >}}

```

The *Examples* section contains executable R code that demonstrates the function's primary use-cases.

::: practice

## Practice

Run the first line of example code from the *Examples* section of the `arrange()` documentation shown above.

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}
```

## {{< var tab_title.hint >}}

You can copy and paste the first line of code directly from the examples section into the editor window.

## {{< var tab_title.solution >}}

```{r}
library(dplyr)

arrange(mtcars, cyl, disp)
```
::::

:::
