---
title: "Environments"
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}
library(knitr)

source(here::here("R", "helpers.R"))

opts_chunk$set(message = FALSE, warning = FALSE, fig.align = "center")
```

## What is an "Environment"

The 'environment' is a loosely organized set of all the objects that R currently has stored in working memory.

## Interacting with the Environment

We can use the `ls()` function to list the contents of the current environment.

```{r}
ls()
```

The `rm()` function will remove an object from the environment.

The following code will remove `x` from the environment.

```{r}
rm(x) # Remove 'x' from the environment
ls()  # Check the results
```

::: practice

## Practice

Use the `rm()` function to remove the `age` object that you created above from your environment, and use `ls()` to check
your work.

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}
```

## {{< var tab_title.solution >}}

```{r}
rm(age)
ls()
```
::::

:::
