---
title: "Logical Comparisons"
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}
library(knitr)

source(here::here("R", "helpers.R"))

opts_chunk$set(message = FALSE,
               warning = FALSE,
               fig.align = "center",
               fig.path = "_figures/01_basic_commands-",
               cache.path = "_cache/01_basic_commands-")
```

We can tests many flavors of logical conditions in R. Logical tests return a logical vector as the result. A logical
vector takes the value of `TRUE` whenever the tested condition is satisified and `FALSE` when the tested condition is
not satisfied.

## Equality

The simplest logical test is an equality check. To check if two objects are equal, we use the 'equality operator', `==`.

```{r}
## Define some objects to play with
y <- 5
x <- 7
w <- 5

### Check equality
y == x
y == w
```

## Greater/Lesser

We can also check the usual greater-than/less-than conditions with `>`, `<`, `>=`, `<=`.

```{r}
y > x  # greater than
y >= x # greater than or equal to
y < x  # less than
y <= x # less than or equal to
```

::: practice

## Practice

What values will the following four expressions return?

:::: {.panel-tabset}
## {{< var tab_title.question >}}

```{r, eval = FALSE}
y > w
y >= w
y < w
y <= w
```

## {{< var tab_title.solution >}}

```{r}
y > w
y >= w
y < w
y <= w
```
::::

:::

## Logical Negation

We can negate any logical condition by prepending the '!' character

```{r}
y > x
!y > x

y == w
!y == w
```

Rather than negating an equality check, we will typically use the special "not-equal" operator, `!=`.

```{r}
y == w
y != w
```

## Combining Conditions

We can create more complex logical conditions with the AND and OR operators: `&` and `|`.

```{r}
y == w & y < x
y == w & y > x
y == w | y > x
```

::: practice

## Practice

Use a single line of code to generate a logical value (i.e., TRUE/FALSE) indicating if the value of the 'weeks' object
you created above is evenly divisible by 7.

:::: {.panel-tabset}
## {{< var tab_title.editor >}}

```{webr-r}
```

## {{< var tab_title.hint >}}

Use `x %% 7` to calculate the remainder after dividing `x` by `7`.

## {{< var tab_title.solution >}}

```{r}
(6 %% 7) == 0
```

If the remainder of dividing `weeks` by 7 is zero, we know that the value of `weeks` is evenly divisible by 7.
::::

:::
