---
title: "Loading Packages"
webr:
  packages:
    - ggplot2
knitr:
  opts_chunk:
    eval: false
---

Once you've installed a new package, you're nearly ready to start using the functionality provided by that package, but
there's still one final step: you must *load* the package into your active R session.

The following code produces an error because we're trying to using the `ggplot()`, `aes()`, and `geom_boxplot()`
functions that are provided by the **ggplot2** package, but we haven't yet loaded that package.

```{r, eval = TRUE, error = TRUE}
ggplot(iris, aes(Species, Petal.Length)) + geom_boxplot()
```

An R package is really just a small piece of software. Like any other software, you only need to install a given R 
package once (just like you only need to install RStudio once), but you'll need to load the package every time you want
to use it in a new R session (like you need to open RStudio every time you want to use it).

We load R packages with the `library()` function.

```{r}
library(dplyr)
```

The `library()` function can only load one package at a time, so you need to call `library()` multiple times to load 
multiple packages.

```{r}
library(dplyr)
library(ggplot2)
```

Running the following code should now produce a simple plot, because we're loaded the **ggplot2** package before trying
to use the functions it provides.

```{webr-r}
library(ggplot2)

ggplot(iris, aes(Species, Petal.Length)) + geom_boxplot()
```
