---
title: "Function Basics"
---

## How Functions are Named

You will almost always be able to quickly identify the functions in R code by the fixed pattern: `FUNCTION_NAME()`. That
is, an R function is called by writing the function name followed imediately by an opening paranthesis. The following list
shows some commonly encounted R functions.

- `c()`
- `list()`
- `ls()`
- `summary()`
- `mean()`
- `lm()`

So, anytime you see a word followed by parenthesis in some R code, you know you've found a function call.

## How Functions Work

In most cases, R functions work in the same way as mathematical functions:

1. Accept some input
1. Perform some operation on the input
1. Return the results of the operation

For example, the following equation represents a linear function of $x$. 

$$
f(x) = 1.5 + 2x
$$

For any value of $x$ that we provide as input, $f(x)$ will first multiply that value by 3 and then add 1.5 to the
resulting product. So, if we let $x = 3$, we get $f(3) = 7.5$.

$$
\begin{align*}
f(3) &= 1.5 + 2 \times 3\\
&= 7.5
\end{align*}
$$

The `mean()` function that we used to motivate these ideas operates through the same conceptual process. In terms of a
mathematical function, you can think of the R function call `mean(1:5)` as supplying the input $x = [1, 2, 3, 4, 5]$ to
a function, $f(x)$, that computes the arithmetic mean of the values in $x$.

If we let $n$ represent the number of values in $x$, we could notate the mathematical representation of the `mean()`
function as follows.

$$
\begin{align}
f(x) = \frac{1}{n}\sum_{i = 1}^{n} x_i
\end{align}
$$ {#eq-mean}

In programming jargon, we would call @eq-mean the *definition* of the mean function. That is, we've defined a tool that 
we can use to compute the mean of any given set of values, but we haven't yet used that tool to compute an actual mean.

To use our defined function to compute a mean, we need to apply $f(x)$ to some input, say, $a = [1, \ldots, 5]$. After
replacing the variable $x$ on the right hand side of @eq-mean with the input data $a$, we can compute the mean, $f(a)$.

$$
\begin{align*}
f(a) &= \frac{1 + 2 + 3 + 4 + 5}{5}\\
&= 3
\end{align*}
$$

Doing the analagous calculation in R would look like the following.

```{r}
a <- 1:5
mean(a)
```

In most of your R analyses, you won't need to worry about defining the functions you use: that work has already been done
by the developers who wrote the packages you're using. You will usually only have to worry about preparing the inputs,
calling an appropriate function, and processing the function's output. 

## Calling Functions 

::: {.column-margin}

:::: reading

[R4DS 2.4: Calling Functions](https://r4ds.hadley.nz/workflow-basics.html#calling-functions)

::::

:::

When you call an R function, you will specify the function inputs by defining values for the function's *arguments*. R
function arguments are named, and most R functions have multiple arguments. You specify the argument values by writing
a comma-separated list of name-value pairs between the parentheses of the function call. For example, the following code
creates a vector of 100 random normal deviates, `dat`, and computes the trimmed mean of `dat` excluding the most extreme
10% of the values.

```{r}
dat <- rnorm(n = 100)
mean(x = dat, trim = 0.05)
```

There are some nuances to how we specify the arguments when we call an R function. Most importantly, we don't always
need to explicitly write out the argument's name, and we don't necessarily need to provide a value for all arguments.
Before we can make much headway on these finer points, however, we need to answer a couple unresolved questions:

1. Where are all these mysterious R functions defined, and how do I access new functions? 
1. How do I know a function's arguments and what values to specify for those arguments? 

In the next two tutorials, you will learn about R packages (the source of most R functions) and R's documentation system
(the means by which you will learn how to use new functions). We will revisit the finer points of calling R functions 
when we discuss documentation.
